### 2013-01-08 ISMB/introduction_ISMB.tex
updated ref bodini

In this paper we introduce \RNApyro, a RNA secondary structure design algorithm that benefits of our recent algorithmic advances \cite{Reinharz:2013aa} to expand our original \RNAensign algorithm \cite{Levin:2012kx}. \RNApyro addresses previous limitations of \RNAensign and offers new functionalities. First, while our previous program had a running time complexity of $\mathcal{O}(n^4)$, \RNApyro has now a linear-time and space complexity that allows him to demonstrate similar speeds to any local search algorithm. Next, \RNApyro is \textit{seed-less}. Unlike \RNAensign, it does not require a seed sequence to start its search. Finally, \RNApyro implements a novel algorithm using weighted sampling techniques \cite{DBLP:journals/corr/abs-1002-0046} that enables us to control, for the first time, \textit{explicitly} the \texttt{C+G}-content of the solution. This functionality is essential because wild sequences within living organisms often present medium or low \texttt{C+G}-content. Presumably to offer better transcription rates and/or structural plasticity. Previous programs do not allow to control this parameter and tend to output sequences with high \texttt{C+G}-contents.

>>>>

In this paper we introduce \RNApyro, a RNA secondary structure design algorithm that benefits of our recent algorithmic advances \cite{Reinharz:2013aa} to expand our original \RNAensign algorithm \cite{Levin:2012kx}. \RNApyro addresses previous limitations of \RNAensign and offers new functionalities. First, while our previous program had a running time complexity of $\mathcal{O}(n^4)$, \RNApyro has now a linear-time and space complexity that allows him to demonstrate similar speeds to any local search algorithm. Next, \RNApyro is \textit{seed-less}. Unlike \RNAensign, it does not require a seed sequence to start its search. Finally, \RNApyro implements a novel algorithm using weighted sampling techniques \cite{Bodini2010} that enables us to control, for the first time, \textit{explicitly} the \texttt{C+G}-content of the solution. This functionality is essential because wild sequences within living organisms often present medium or low \texttt{C+G}-content. Presumably to offer better transcription rates and/or structural plasticity. Previous programs do not allow to control this parameter and tend to output sequences with high \texttt{C+G}-contents.
